Lifespan analysis

### 2023-07-19 stats/lifespan.Rmd
adjust lifespan plot (blue spaghetti)

@@

@@

# PLOT

```{r plot}
ggplot() +

  geom_jitter(
    data = mdata, 
    aes(x = age, y = mean_imprecision), 
    col = "darkgrey", alpha = 0.75
  ) +

  geom_smooth(
    data = pred, 
    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
  ) +

  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.75, size = 1) +
  # geom_vline(xintercept = cps$lowerCrI, linetype = "dotted", alpha = 0.5, size = 1) +
  # geom_vline(xintercept = cps$upperCrI, linetype = "dotted", alpha = 0.5, size = 1) +

@@

@@

# ZOOM IN
ggplot() +

  geom_jitter(
    data = mdata, 
    aes(x = age, y = mean_imprecision), 
    col = "darkgrey", alpha = 0.75
  ) +

  geom_smooth(
    data = pred, 
    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
  ) +

  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.75, size = 1) +

  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 0.5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +

  coord_cartesian(xlim = c(3, 10), ) +

  labs(x = "Age in years", y = "Average imprecision in target width")
```

>>>>

```{r variation}
lifespan_data %>% 
  group_by(age_group) %>%
  summarise(
    imprecision_mean = mean(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_sd = sd(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_min = min(click_dist_balloons, na.rm = T),
    imprecision_max = max(click_dist_balloons, na.rm = T),
  )
```

@@

pred <- pred %>% clean_names()

@@

# PLOT
```{r plot}
# mgaussianprocess <- readRDS("../saves/lifespan_mgaussianprocess.rds")
# cps <- readRDS("../saves/lifespan_ibeast_cps.rds")

# https://cran.r-project.org/web/packages/tidybayes/vignettes/tidy-brms.html
mdata %>%
  add_epred_draws(mgaussianprocess, ndraws = 100) %>%

  ggplot(aes(x = age, y = mean_imprecision)) +

  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +

  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +

  geom_smooth(data = pred, aes(x = age, y = estimate), stat = "identity", col = "black", size = 0.75) +

  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +

@@

  # ## to zoom in
  # coord_cartesian(xlim = c(3, 10)) +
  # scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 1)) +

@@

# ggsave("../figures/lifespan.png", width = 7, height = 4)
# ggsave("../figures/lifespan.pdf", width = 7, height = 4)
```
